A geo-referenced micro-data set of real estate listings for Spain's three largest cities

### 2023-05-19 EPB/main_EPB_v0.tex
Resubmission to EPB

\runninghead{Rey-Blanco \emph{et al}.}

\author{D. Rey-Blanco\affilnum{1}, P. Arbues\affilnum{1}, F.
López\affilnum{2}, A. Páez*\affilnum{3}}

\affiliation{\affilnum{1}{Idealista, Plaza de las Cortes 5, 28014
Madrid, Spain}\\\affilnum{2}{Facultad de CC de la Empresa, C/ Real, 3.
30201 Cartagena, Murcia, Spain}\\\affilnum{3}{School of Earth,
Environment and Society, McMaster University, 1280 Main St W, Hamilton,
Ontario L8S 4K1 Canada}}

\corrauth{Antonio Páez, School of Earth, Environment and Society,
McMaster University, 1280 Main St W, Hamilton, Ontario L8S 4K1 Canada.}

\email{\href{mailto:paezha@mcmaster.ca}{\nolinkurl{paezha@mcmaster.ca}}}

@@

We are also witnessing a growing interest in open data in geography and
data science \citep{arribasl2021editorial, arribas2021} using
reproducible or replicable research \citep{paez2021open}. But to work
openly in science, it is necessary to have free software and open data.
While great efforts have been made to make free software available to
researchers (e.g., R or Python), not much data is currently out in the
open. In the particular case of the real estate market, to our
knowledge, there are few open micro-data sets of housing markets
available \citep{Song2021}.

To overcome these limitations, this paper presents a sort description of
an open micro-data set of geo-referenced dwelling listings. The data
have been provided by the Idealista
company\footnote{Idealista is the major real estate listing website in Spain, and present in other southern european countries as Italy and Portugal}
and contain information about 189,923 dwellings located in Spain's three
largest cities. To date, this data product is the biggest open
geo-referenced micro-data set of the housing market in Spain. Moreover,
the data set has been supplied directly by Idealista, and therefore is
clean and free of download errors. The listings have been enriched with
official information from the Spanish cadastre along with other relevant
geographical features, such as distance to urban points of interest. The
data set is distributed as an R package, named `idealista18', which can
be accessed from the Github
repository\footnote{The direct URL to the GitHub repository is \url{https://github.com/paezha/idealista18}}.

@@

\begin{figure}
\centering
\includegraphics{EPB_files/figure-latex/unnamed-chunk-1-1.pdf}
\caption{\label{fig:all-polygons}Quantile maps of the number of
dwellings in each neighborhood. Boundary for Barcelona (Left), Madrid
(Center), and Valencia (Right).}
\end{figure}

>>>>

\runninghead{author \emph{et al}.}

\author{\affilnum{}}

\affiliation{}

@@

We are also witnessing a growing interest in open data in geography and
data science \citep{arribasl2021editorial, arribas2021} using
reproducible or replicable research
\citep{paez2021open, brunsdon2021opening}. But to work openly in
science, it is necessary to have free software and open data. While
great efforts have been made to make free software available to
researchers (e.g., R or Python), data regarding real estate markets tend
to be treated as confidential, and there are still few open micro-data
sets of housing markets available \citep{Song2021}.

To contribute to the growing inventory of international micro-data sets
of real estate markets, this paper introduces an open micro-data set of
geo-referenced dwelling listings. The data have been provided by the
Idealista
company\footnote{Idealista is the major real estate listing website in Spain, and present in other southern european countries as Italy and Portugal}
and contain information about 189,923 dwellings located in Spain's three
largest cities. To date, this data product is the biggest open
geo-referenced micro-data set of the housing market in Spain. Moreover,
the data set has been supplied directly by Idealista, and therefore is
clean and free of download errors. However, in order to be able to share
publicly the data we have slightly modified some variables by applying
some random noise which will not bias the main results derived from its
usage.

This micro-data set is expected to be used as a benchmark dataset to
test empirical methods in a reproducible fashion. Applied and
theoretical researchers on real estate mass appraisal and valuation
methods might use this dataset to canonically compare the performance of
their proposed comparable and hedonic models, among others. The data can
also be used to study the segmentation of housing submarkets and related
topics such as the impact of suburban areas on house prices. The
listings have been enriched with official information from the Spanish
cadastre along with other relevant geographical features, such as
distance to urban points of interest. In any case, the data might be
easily extended by spatially joining other datasets that contain
information at administrative, census tract, or postal code levels.

The data set is distributed as an R package, name \{idealista18\}, which
can be accessed from a public Github
repository\footnote{The direct URL to the GitHub repository is \url{https://github.com/paezha/idealista18}}.
The database idealista18 is made available under the
\href{http://opendatacommons.org/licenses/odbl/1.0/}{Open Database License}.
For transparency, we also share the randomisation process applied to the
original data in the aforementioned Github repository.

@@

\begin{figure}
\centering
\includegraphics{main_EPB_v0_files/figure-latex/unnamed-chunk-1-1.pdf}
\caption{\label{fig:all-polygons}Quantile maps of the number of
dwellings in each neighborhood. Boundary for Barcelona (Left), Madrid
(Center), and Valencia (Right).}
\end{figure}
